Survival - frequentist

### 2020-11-03 manuscript/analysis_brms.Rmd
Inching towards a complete draft

```{r}
#Marking the results as suspicious because there was a divergence...
draws <- tidy_draws(fit_survival_base)
hypothesis_res_list[["hcq_az_survival_base"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary",
    estimand = "logit(survival)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary",
    estimand = "logit(survival)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_binary",
    estimand = "logit(survival)",
    hypothesis = hypotheses$favipiravir_reduces_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_survival_base_7)
hypothesis_res_list[["hcq_az_survival_base_7"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary_7",
    estimand = "logit(survival)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary_7",
    estimand = "logit(survival)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_binary_7",
    estimand = "logit(survival)",
    hypothesis = hypotheses$favipiravir_reduces_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_survival_base_28)
hypothesis_res_list[["hcq_az_survival_base_28"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary_28",
    estimand = "logit(survival)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary_28",
    estimand = "logit(survival)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_binary_28",
    estimand = "logit(survival)",
    hypothesis = hypotheses$favipiravir_reduces_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_discharged_base)
hypothesis_res_list[["hcq_az_discharged_base"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_binary",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$favipiravir_increases_discharged,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_discharged_base_7)
hypothesis_res_list[["hcq_az_discharged_base_7"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary_7",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary_7",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_binary_7",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$favipiravir_increases_discharged,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_discharged_base_28)
hypothesis_res_list[["hcq_az_discharged_base_28"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary_28",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary_28",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_binary_28",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$favipiravir_increases_discharged,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_outcome_base)
hypothesis_res_list[["hcq_az_outcome_base"]] <- rbind(
  # Death 
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_hcqTRUE,
    model = "brms_categorical",
    estimand = "logit(death)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_azTRUE,
    model = "brms_categorical",
    estimand = "logit(death)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_favipiravirTRUE,
    model = "brms_categorical",
    estimand = "logit(death)",
    hypothesis = hypotheses$favipiravir_reduces_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity"
  ),
  # Discharged
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_hcqTRUE,
    model = "brms_categorical",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_azTRUE,
    model = "brms_categorical",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_favipiravirTRUE,
    model = "brms_categorical",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$favipiravir_increases_discharged,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity"
  )
)
```

>>>>

```{r}
#Marking the results as suspicious because there was a divergence...
draws <- tidy_draws(fit_survival_base)
hypothesis_res_list[["hcq_az_survival_base"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary",
    estimand = "logit(survival)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary",
    estimand = "logit(survival)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_binary",
    estimand = "logit(survival)",
    hypothesis = hypotheses$favipiravir_reduces_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_survival_base_7)
hypothesis_res_list[["hcq_az_survival_base_7"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary_7",
    estimand = "logit(survival)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary_7",
    estimand = "logit(survival)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_binary_7",
    estimand = "logit(survival)",
    hypothesis = hypotheses$favipiravir_reduces_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_survival_base_28)
hypothesis_res_list[["hcq_az_survival_base_28"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary_28",
    estimand = "logit(survival)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary_28",
    estimand = "logit(survival)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_binary_28",
    estimand = "logit(survival)",
    hypothesis = hypotheses$favipiravir_reduces_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_discharged_base)
hypothesis_res_list[["hcq_az_discharged_base"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_binary",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$favipiravir_increases_discharged,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_discharged_base_7)
hypothesis_res_list[["hcq_az_discharged_base_7"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary_7",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary_7",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_binary_7",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$favipiravir_increases_discharged,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_discharged_base_28)
hypothesis_res_list[["hcq_az_discharged_base_28"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary_28",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary_28",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_binary_28",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$favipiravir_increases_discharged,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_outcome_base)
hypothesis_res_list[["hcq_az_outcome_base"]] <- rbind(
  # Death 
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_hcqTRUE,
    model = "brms_categorical",
    estimand = "logit(death)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_azTRUE,
    model = "brms_categorical",
    estimand = "logit(death)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_favipiravirTRUE,
    model = "brms_categorical",
    estimand = "logit(death)",
    hypothesis = hypotheses$favipiravir_reduces_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  # Discharged
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_hcqTRUE,
    model = "brms_categorical",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_azTRUE,
    model = "brms_categorical",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_favipiravirTRUE,
    model = "brms_categorical",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$favipiravir_increases_discharged,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  )
)
```

### 2020-11-03 manuscript/competing_risks.Rmd
Inching towards a complete draft

@@

```{r}
hypothesis_res_all <- do.call(rbind, hypothesis_res_list)
write_csv(hypothesis_res_all, path = paste0(cache_dir, "/competing_risks_res.csv"))
```

>>>>

```{r}
f_competing_hcq_az_fpv <- update.formula(f_competing_hcq_az, . ~ . + took_favipiravir)
fit_competing_hcq_az_fpv <- coxph(f_competing_hcq_az_fpv, data = data_surv, id = patient_id)

fit_competing_hcq_az_fpv

hypothesis_res_list[["competing_hcq_az_fpv"]] <-
  rbind(
  frequentist_hypothesis_res_from_coxph(hypotheses$favipiravir_reduces_death, fit_competing_hcq_az_fpv,
                                        coefficient_name = "took_favipiravirTRUE", transition = "1:3", adjusted = "age, sex, hcq, az"),
  frequentist_hypothesis_res_from_coxph(hypotheses$favipiravir_increases_discharged, fit_competing_hcq_az_fpv,
                                        coefficient_name = "took_favipiravirTRUE", transition = "1:2", adjusted = "age, sex, hcq, az")
  )
hypothesis_res_list[["competing_hcq_az_fpv"]]
```

@@

```{r}
hypothesis_res_all <- do.call(rbind, hypothesis_res_list)
write_csv(hypothesis_res_all, path = here::here("manuscript", "/competing_risks_res.csv"))
```
